Exploring Income Inequality in US after and before financial crises: Analysis

### 2024-04-14 paper/paper.qmd
Update paper.qmd

---
title: "Exploring Income Inequality in US after financial crises: Analysis"
subtitle: "Insights from 2002 to 2019"
author: "Dong Jun Yoon"
thanks: "Code and data are available at: https://github.com/DJY1231/Exploring-Income-Inequality-in-US.git"
date: today
date-format: long
abstract: "This paper investigates income inequality in the United States from 2002 to 2019 using data from the United States Census and the World Inequality Database (WID). Throughout the paper, we will explore trends in income inequality, examining whether it is increasing or decreasing over time, and how the Great Recession of 2007-2009 affected income inequality. We will utilize data analysis and regression modeling to investigate these trends. Investigating these trends is significant, as it could assist policymakers or the government in developing strategies that could decrease the inequalities occurring within the country. As a result, this report may be used to help promote social and economic equity in the United States."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Data {#sec-data}

## Data Source
The first and second data is gathered from the United States Census Bureau, where the first dataset introduces the income share by each social class over time: 2002 to 2019 in the United States. The second data illustrates the median household income based on race and year.

@@

## Variables of Interest
```{r}
# Load the necessary library
library(knitr)

@@

## Data Visualization
```{r}
library(ggplot2)

@@

```{r}
# Load necessary libraries
library(readr)
library(ggplot2)
library(dplyr)
library(scales)

@@

# Results
The regression results are as following:
```{r}
# Load necessary libraries
if (!require(dplyr)) install.packages("dplyr")
if (!require(stargazer)) install.packages("stargazer")
if (!require(performance)) install.packages("performance")

>>>>

---
title: "Exploring Income Inequality in US after and before financial crises: Analysis"
subtitle: "Insights from 2002 to 2019"
author: "Dong Jun Yoon"
thanks: "Code and data are available at: https://github.com/DJY1231/Exploring-Income-Inequality-in-US.git"
date: today
date-format: long
abstract: "This paper investigates income inequality in the United States from 2002 to 2019 using data from the United States Census and the World Inequality Database (WID). Throughout the paper, we will explore trends in income inequality, examining whether it is increasing or decreasing over time, and how the Great Recession of 2007-2009 affected income inequality. We will utilize data analysis and regression modeling to investigate these trends. Investigating these trends is significant, as it could assist policymakers or the government in developing strategies that could decrease the inequalities occurring within the country. As a result, this report may be used to help promote social and economic equity in the United States."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Data {#sec-data}
## Data Source
The first and second data is gathered from the United States Census Bureau, where the first dataset introduces the income share by each social class over time: 2002 to 2019 in the United States. The second data illustrates the median household income based on race and year.

@@

## Variables of Interest
```{r, echo = FALSE}
# Load the necessary library
library(knitr)

@@

## Data Visualization
```{r, echo = FALSE}
library(ggplot2)

@@

```{r, echo = FALSE}
# Load necessary libraries
library(readr)
library(ggplot2)
library(dplyr)
library(scales)

@@

# Results
The regression results are as following:
```{r, echo = FALSE}
# Load necessary libraries
if (!require(dplyr)) install.packages("dplyr")
if (!require(stargazer)) install.packages("stargazer")
if (!require(performance)) install.packages("performance")
